Project Uccle

### 2020-05-23 chapter1.Rmd
divided not-common analysis and some more analysis

library(spec)
pgram <- spec.pgram(build_ts(seis.h, start=as_datetime('2018-11-01T00:00:00'), end=as_datetime('2020-03-01T00:00:00')), main="periodgram", detrend=F, demean=T, na.action=na.aggregate)
topfreq <- pgram$freq[order(pgram$spec, decreasing = T)][1:100]
topseas <- 1/topfreq
topseas.h <- topseas/3600

>>>>

pgram <- spec.pgram(build_ts(seis.h, start=as_datetime('2018-11-01T00:00:00'), end=as_datetime('2020-03-01T00:00:00')), main="periodgram", detrend=F, demean=T, na.action=na.aggregate)
topfreq <- pgram$freq[order(pgram$spec, decreasing = T)][1:100]
topseas <- 1/topfreq
topseas.h <- topseas/3600

### 2020-05-23 project.Rmd
divided not-common analysis and some more analysis

```{r libraries, include=FALSE}
library(knitr)
opts_chunk$set(warning = F, message = F)
library(stringi) # %s+%
library(lubridate) # floor_date
library(xts) # zoo
library(fpp) # auto.arima
# library(gridExtra) # for gg-plotting multiple plots
library(cowplot) # for plot_grid
library(car) # qqPlot
library(tidyverse) # map_df, read_csv, group_by, summarize
library(tsbox) # https://cran.r-project.org/web/packages/tsbox/vignettes/tsbox.html
print_dec <- function(x, decimals=2) trimws(format(round(x, decimals), nsmall=decimals))

setwd("/media/data/Documents/Uni/spatiotemp/villalobos/project/")
```

```{r import dataset, include=FALSE}
if (!exists("domain")) {
  # UCCS
  domain <- c(-350000,350000); pattern <- "UCCS.*\\.csv"; name <- "UCCS"; description <- "Uccle, Bruxelles"; proj_file <- 'proj.uccs.RData'
  # MEMS
  domain <- c(-7200,7200); pattern <- "MEM.*\\.csv"; name <- "MEM"; description <- "Membach"; proj_file <- 'proj.mems.RData'
}
if (exists("proj_file")) {
  load(paste0("/media/data/Documents/Uni/spatiotemp/villalobos/project/", proj_file))
  # save.image(paste0("/media/data/Documents/Uni/spatiotemp/villalobos/project/", proj_file))
}
seis <-
  list.files(path="csv/", pattern=pattern) %>%
  map_df(~read_csv("csv/" %s+% .))
```

@@

block_start <- NULL
block_end <- NULL
blocks <- data.frame(start=integer(), end=integer())
for (i in 1:length(seis.missing.ids)) {
  if (is.null(block_start)) {
    block_start <- seis.missing.ids[i]
    block_end <- seis.missing.ids[i]
  } else if ((block_end + 1) == seis.missing.ids[i]) {
    block_end <- seis.missing.ids[i]
  } else {
    blocks[nrow(blocks) + 1, ] <- c(block_start, block_end)
    block_start <- seis.missing.ids[i]
    block_end <- seis.missing.ids[i]
  }
}
blocks[nrow(blocks) + 1, ] <- c(block_start, block_end)
blocks$interval <- hours(blocks$end - blocks$start + 1)
blocks$start <- seis.first.second + hours(blocks$start)
blocks$end <- seis.first.second + hours(blocks$end)
plot(c(rbind(blocks$start, blocks$end, NA)), rep(hour(blocks$interval), each=3),
     col=ifelse(blocks$interval<3600, "darkgreen", "darkred"),
     main="Consecutive hours of missing values",
     ylab="Hours", xlab="Interval start",
     type="l", lwd=10,
     xaxt="n", xlim=c(min(seis$utc_second), max(seis$utc_second))
     )
axis.POSIXct(1, at=seq.POSIXt(from=min(seis$utc_second), to=max(seis$utc_second), by = "1 month"), format="%m-%y", cex=0.8)
text(x=blocks$start, y=hour(blocks$interval), labels = paste0(format(blocks$start, "%y-%m-%d %H:%M")), cex=0.9, pos=2)
text(x=blocks$end, y=hour(blocks$interval), labels = paste0(format(blocks$end, "%y-%m-%d %H:%M")), cex=0.9, pos=4)
text(x=blocks$start + make_difftime(hour=sapply(hour(blocks$interval), "/", y=2)), y=hour(blocks$interval), labels = paste0(hour(blocks$interval), "H"), cex=0.9, pos=3)
remove(seis.complete, seis.missing.ids)

@@

@@

```{r arima}
to_test <- list(
  #c(0,0,0,0,0,1),  # BAD, Box-Pierce = 0
  #c(0,0,0,0,0,2),  # BAD, Box-Pierce = 0
  #c(0,0,0,0,1,1),  # nice, Box-Pierce = 0
  c(0,0,0,0,1,2),
  #c(0,0,0,0,1,3),  # CAN'T BE DONE: 3*168 = 504 > 350 (limit of arima on r)
  #c(0,1,0,0,0,1),  # BAD, Box-Pierce = 0
  c(0,1,0,0,1,1),
  c(0,1,0,0,1,2),
  c(2,0,0,0,1,0),  # hint from auto.arima D=1
  c(5,0,0,0,1,0),  # hint from auto.arima D=1
  c(3,1,1,0,1,0),  # hint from auto.arima D=1 d=1
  c(3,1,1,0,1,1),  # after hint then ACF + PACF
  c(4,1,2,0,1,0),  # hint from auto.arima d=1, D=1, max.p=5, max.q=2, max.P=5, max.Q=2, max.order=10
  c(4,1,2,0,1,1)  # after hint then ACF + PACF
)
if (!exists("models")){
  models <- list()
}
for (model in to_test) {
  # model <- c(4,1,2,0,1,0)
  fit.name <- paste0("fit", paste0(model, collapse = ""))
  forecast.name <- paste0("forecast", paste0(model, collapse = ""))
  print("SARIMA(" %s+% paste0(model[1:3], collapse = ",") %s+% ")(" %s+% paste0(model[4:6], collapse = ",") %s+% ")[" %s+% frequency(seis.h.train) %s+% "]")
  if (!(fit.name %in% names(models))) {
    models[[fit.name]] <- Arima(seis.h.train, model[1:3], model[4:6])
  }
  if (!(forecast.name %in% names(models))) {
    models[[forecast.name]] <- forecast(models[[fit.name]], h=168*18)
  }
}
#models[["fitauto"]] <- auto.arima(seis.h.train, D=1, approx=F, trace = T)
#models[["forecastauto"]] <- forecast(models[["fitauto"]], h=168*18)  
#models[["fit311010"]] <- models[["fitauto"]]
#models[["fit412010"]] <- fit
#models[["forecast412010"]] <- forecast(models[["fit412010"]], h=168*18)

# 000012 better than 000011, Box-Pierce = 0
plotting.model <- models[["fit000012"]]
plotting.forecast <- models[["forecast000012"]]
# 010011 somehow better somehow worst than 000012, Box-Pierce = 0
plotting.model <- models[["fit010011"]]
plotting.forecast <- models[["forecast010011"]]
# 010012 , Box-Pierce = 
plotting.model <- models[["fit010012"]]
plotting.forecast <- models[["forecast010012"]]
# 311010 , Box-Pierce = 
plotting.model <- models[["fit311010"]]
plotting.forecast <- models[["forecast311010"]]
# 311011 , Box-Pierce = 
plotting.model <- models[["fit311011"]]
plotting.forecast <- models[["forecast311011"]]

checkresiduals(plotting.model)
residuals.acf <- autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*5)) + scale_x_continuous() + labs(title = paste0("Series: residuals of ", plotting.forecast$method))
residuals.pacf <- autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*5)) + scale_x_continuous() + labs(title = paste0("Series: residuals of ", plotting.forecast$method))
plot_grid(residuals.acf, residuals.pacf, nrow=2)
plot_forecast(plotting.forecast) + 
  autolayer(seis.h.test, series="Original")
plots <- show_overlap_and_diff(
  seis.h.train, plotting.forecast$fitted, xlab=seasonality.xlab,
  base.desc = "original series",
  compare.desc = "reconstructed series",
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="% over ts span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)
accuracy(plotting.forecast, seis.h.test)

plotting.model <- models[["fit010012"]]
plotting.forecast <- models[["forecast010012"]]
checkresiduals(plotting.model)
residuals.acf <- autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*5)) + scale_x_continuous() + labs(title = paste0("Series: residuals of ", plotting.forecast$method))
residuals.pacf <- autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*5)) + scale_x_continuous() + labs(title = paste0("Series: residuals of ", plotting.forecast$method))
plot_grid(residuals.acf, residuals.pacf, nrow=2)
plot_forecast(plotting.forecast) + 
  autolayer(seis.h.test, series="Original")
plots <- show_overlap_and_diff(
  seis.h.train, plotting.forecast$fitted, xlab=seasonality.xlab,
  base.desc = "original series",
  compare.desc = "reconstructed series",
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="% over ts span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)
accuracy(plotting.forecast, seis.h.test)

plotting.model <- models[["fit412010"]]
plotting.forecast <- models[["forecast412010"]]
checkresiduals(plotting.model)
residuals.acf <- autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*5)) + scale_x_continuous() + labs(title = paste0("Series: residuals of ", plotting.forecast$method))
residuals.pacf <- autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*5)) + scale_x_continuous() + labs(title = paste0("Series: residuals of ", plotting.forecast$method))
plot_grid(residuals.acf, residuals.pacf, nrow=2)
plot_forecast(plotting.forecast) + 
  autolayer(seis.h.test, series="Original") 
plots <- show_overlap_and_diff(
  seis.h.train, plotting.forecast$fitted, xlab=seasonality.xlab,
  base.desc = "original series",
  compare.desc = "reconstructed series",
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="% over ts span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)
accuracy(plotting.forecast, seis.h.test)

plotting.model <- models[["fit500010"]]
plotting.forecast <- models[["forecast500010"]]
checkresiduals(plotting.model)
residuals.acf <- autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*5)) + scale_x_continuous() + labs(title = paste0("Series: residuals of ", plotting.forecast$method))
residuals.pacf <- autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*5)) + scale_x_continuous() + labs(title = paste0("Series: residuals of ", plotting.forecast$method))
plot_grid(residuals.acf, residuals.pacf, nrow=2)
plot_forecast(plotting.forecast) + 
  autolayer(seis.h.test, series="Original") 
plots <- show_overlap_and_diff(
  seis.h.train, plotting.forecast$fitted, xlab=seasonality.xlab,
  base.desc = "original series",
  compare.desc = "reconstructed series",
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="% over ts span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)
accuracy(plotting.forecast, seis.h.test)

for (model in to_test) {
  # model <- c(4,1,2,0,1,0)
  fit.name <- paste0("fit", paste0(model, collapse = ""))
  forecast.name <- paste0("forecast", paste0(model, collapse = ""))
  print("SARIMA(" %s+% paste0(model[1:3], collapse = ",") %s+% ")(" %s+% paste0(model[4:6], collapse = ",") %s+% ")[" %s+% frequency(seis.h.train) %s+% "]")
  if ((fit.name %in% names(models))) {  if ((forecast.name %in% names(models))) {
    plotting.model <- models[[fit.name]]
    plotting.forecast <- models[[forecast.name]]
    checkresiduals(plotting.model)
    residuals.acf <- autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*5)) + scale_x_continuous() + labs(title = paste0("Series: residuals of ", plotting.forecast$method))
    residuals.pacf <- autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*5)) + scale_x_continuous() + labs(title = paste0("Series: residuals of ", plotting.forecast$method))
    plot_grid(residuals.acf, residuals.pacf, nrow=2)
    plot_forecast(plotting.forecast) + 
      autolayer(seis.h.test, series="Original") 
    plots <- show_overlap_and_diff(
      seis.h.train, plotting.forecast$fitted, xlab=seasonality.xlab,
      base.desc = "original series",
      compare.desc = paste0("refit with ", plotting.forecast$method),
      overlap.ylab = "Mean hourly movement (nm)",
      diff.title = "Difference between ts",
      diff.ylab = "nm", diff.ylab.sec="% over ts span",
      diff.ylab.sec.accuracy = .01
    )
    plot_grid(plots[[1]], plots[[2]], nrow = 2)
    accuracy(plotting.forecast, seis.h.test)
  }}
}
qqPlot(models[["fit500010"]]$residuals)
```

```{r}
#fit <- auto.arima(seis.h.train, d=1, D=1, max.p=5, max.q=2, max.P=5, max.Q=2, max.order=10, trace = T, parallel = T)
```
# D=1 m=24
 Fitting models using approximations to speed things up...

 ARIMA(2,0,2)(1,1,1)[24] with drift         : Inf
 ARIMA(0,0,0)(0,1,0)[24] with drift         : 111462.7
 ARIMA(1,0,0)(1,1,0)[24] with drift         : 101954.4
 ARIMA(0,0,1)(0,1,1)[24] with drift         : Inf
 ARIMA(0,0,0)(0,1,0)[24]                    : 111460.9
 ARIMA(1,0,0)(0,1,0)[24] with drift         : 102426.5
 ARIMA(1,0,0)(2,1,0)[24] with drift         : 101379
 ARIMA(1,0,0)(2,1,1)[24] with drift         : Inf
 ARIMA(1,0,0)(1,1,1)[24] with drift         : Inf
 ARIMA(0,0,0)(2,1,0)[24] with drift         : 110647.6
 ARIMA(2,0,0)(2,1,0)[24] with drift         : 101332.9
 ARIMA(2,0,0)(1,1,0)[24] with drift         : 101878.7
 ARIMA(2,0,0)(2,1,1)[24] with drift         : Inf
 ARIMA(2,0,0)(1,1,1)[24] with drift         : Inf
 ARIMA(3,0,0)(2,1,0)[24] with drift         : 101317.9
 ARIMA(3,0,0)(1,1,0)[24] with drift         : 101858.5
 ARIMA(3,0,0)(2,1,1)[24] with drift         : Inf
 ARIMA(3,0,0)(1,1,1)[24] with drift         : Inf
 ARIMA(4,0,0)(2,1,0)[24] with drift         : 101302.7
 ARIMA(4,0,0)(1,1,0)[24] with drift         : 101845
 ARIMA(4,0,0)(2,1,1)[24] with drift         : Inf
 ARIMA(4,0,0)(1,1,1)[24] with drift         : Inf
 ARIMA(5,0,0)(2,1,0)[24] with drift         : 101305.4
 ARIMA(4,0,1)(2,1,0)[24] with drift         : 101304.5
 ARIMA(3,0,1)(2,1,0)[24] with drift         : 101307.7
 ARIMA(5,0,1)(2,1,0)[24] with drift         : 101307.7
 ARIMA(4,0,0)(2,1,0)[24]                    : 101300.7
 ARIMA(4,0,0)(1,1,0)[24]                    : 101843
 ARIMA(4,0,0)(2,1,1)[24]                    : Inf
 ARIMA(4,0,0)(1,1,1)[24]                    : Inf
 ARIMA(3,0,0)(2,1,0)[24]                    : 101316
 ARIMA(5,0,0)(2,1,0)[24]                    : 101303.4
 ARIMA(4,0,1)(2,1,0)[24]                    : 101302.4
 ARIMA(3,0,1)(2,1,0)[24]                    : 101305.8
 ARIMA(5,0,1)(2,1,0)[24]                    : 101305.7

 Now re-fitting the best model(s) without approximations...

 ARIMA(4,0,0)(2,1,0)[24]                    : 101586.6

 Best model: ARIMA(4,0,0)(2,1,0)[24]

# d=1, D=1, max.p=5, max.q=2, max.P=5, max.Q=2, max.order=10 m=168
 Fitting models using approximations to speed things up...

 ARIMA(2,1,2)(1,1,1)[168]                    : Inf
 ARIMA(0,1,0)(0,1,0)[168]                    : 122379.8
 ARIMA(1,1,0)(1,1,0)[168]                    : Inf
 ARIMA(0,1,1)(0,1,1)[168]                    : Inf
 ARIMA(0,1,0)(1,1,0)[168]                    : Inf
 ARIMA(0,1,0)(0,1,1)[168]                    : Inf
 ARIMA(0,1,0)(1,1,1)[168]                    : Inf
 ARIMA(1,1,0)(0,1,0)[168]                    : 121638
 ARIMA(1,1,0)(0,1,1)[168]                    : Inf
 ARIMA(1,1,0)(1,1,1)[168]                    : Inf
 ARIMA(2,1,0)(0,1,0)[168]                    : 121468.5
 ARIMA(2,1,0)(1,1,0)[168]                    : Inf
 ARIMA(2,1,0)(0,1,1)[168]                    : Inf
 ARIMA(2,1,0)(1,1,1)[168]                    : Inf
 ARIMA(3,1,0)(0,1,0)[168]                    : 121452.9
 ARIMA(3,1,0)(1,1,0)[168]                    : Inf
 ARIMA(3,1,0)(0,1,1)[168]                    : Inf
 ARIMA(3,1,0)(1,1,1)[168]                    : Inf
 ARIMA(4,1,0)(0,1,0)[168]                    : 121403.9
 ARIMA(4,1,0)(1,1,0)[168]                    : Inf
 ARIMA(4,1,0)(0,1,1)[168]                    : Inf
 ARIMA(4,1,0)(1,1,1)[168]                    : Inf
 ARIMA(5,1,0)(0,1,0)[168]                    : 121361.7
 ARIMA(5,1,0)(1,1,0)[168]                    : Inf
 ARIMA(5,1,0)(0,1,1)[168]                    : Inf
 ARIMA(5,1,0)(1,1,1)[168]                    : Inf
 ARIMA(5,1,1)(0,1,0)[168]                    : 118580.2
 ARIMA(5,1,1)(1,1,0)[168]                    : Inf
 ARIMA(5,1,1)(0,1,1)[168]                    : Inf
 ARIMA(5,1,1)(1,1,1)[168]                    : Inf
 ARIMA(4,1,1)(0,1,0)[168]                    : 118580.3
 ARIMA(5,1,2)(0,1,0)[168]                    : 118581.5
 ARIMA(4,1,2)(0,1,0)[168]                    : 118553.1
 ARIMA(4,1,2)(1,1,0)[168]                    : Inf
 ARIMA(4,1,2)(0,1,1)[168]                    : Inf
 ARIMA(4,1,2)(1,1,1)[168]                    : Inf
 ARIMA(3,1,2)(0,1,0)[168]                    : 118642.8
 ARIMA(3,1,1)(0,1,0)[168]                    : 119155

 Now re-fitting the best model(s) without approximations...

 ARIMA(4,1,2)(0,1,0)[168]                    : 122838.5

 Best model: ARIMA(4,1,2)(0,1,0)[168]

```{r eval=FALSE, include=FALSE}

autoplot(acf(seis.h.train.ds, plot=F, lag.max = 168*2)) + scale_x_continuous()
autoplot(pacf(seis.h.train.ds, plot=F, lag.max = 168*2)) + scale_x_continuous()

qqPlot(fit$residuals)
gghistogram(fit$residuals)
Box.test(fit$residuals, type="Box-Pierce")
fit.forec <- forecast(fit, h=24*10)
plot(fit.forec, xlim=c(250, 300))

frequency(seis.h.train)
p<-168;d<-0;q<-0;P<-0;D<-1;Q<-0;
paste0("ARIMA(", p, ",", d, ",", q, ")(", P, ",", D, ",", Q, ")_", frequency(seis.h.train))
fit <- Arima(seis.h.train, order=c(p,d,q), seasonal=c(P,D,Q))
fit
#Diagnostics
tsdisplay(residuals(fit), lag.max=168*2)

p<-1;d<-0;q<-2;P<-1;D<-0;Q<-2;
fit <- Arima(seis.h.train, order=c(p,d,q), seasonal=c(P,D,Q))
#Diagnostics
tsdisplay(residuals(fit))
forecast()

```{r mstl on msts}
seis.h.train.m <- msts(seis.h.train, c(24, 168))
seis.mstl <- seis.h.train.m %>% mstl(s.window="periodic") #c(15, 7))
seis.mstl.fc <- forecast(seis.mstl, h=168*18)

autoplot(seis.mstl) + xlab("Week")
plot(seis.mstl[,2], main="trend")
lines(trend.s, col="red")
plot(rowSums(seis.mstl[,3:4]), main="seasonality",type="l")
lines(seasonality, col="red")
plot(seis.mstl[,5],  main="residuals")
lines(residuals, col="red")

plotting.model <- seis.mstl
plotting.forecast <- seis.mstl.fc
checkresiduals(plotting.model[,5])
Box.test(plotting.forecast$model$residuals, type="L")
residuals.acf <- autoplot(acf(plotting.model[,5], na.action = na.pass, plot=F, lag.max=168*5)) + scale_x_continuous() + labs(title = paste0("Series: residuals of ", plotting.forecast$method))
residuals.pacf <- autoplot(pacf(plotting.model[,5], na.action = na.pass, plot=F, lag.max=168*5)) + scale_x_continuous() + labs(title = paste0("Series: residuals of ", plotting.forecast$method))
plot_grid(residuals.acf, residuals.pacf, nrow=2)

plot_forecast(plotting.forecast) + 
  autolayer(seis.h.test, series="Original") +
  xlim(52, 70) + ylim(0, 8750)
plot_forecast(plotting.forecast) + 
  autolayer(seis.h.test, series="Original")
plots <- show_overlap_and_diff(
  seis.h.train, plotting.forecast$fitted, xlab=seasonality.xlab,
  base.desc = "train series",
  compare.desc = paste0("refit with ", plotting.forecast$method),
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="% over ts span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)
plots <- show_overlap_and_diff(
  seis.h.test[1:length(plotting.forecast$mean)], plotting.forecast$mean, xlab=seasonality.xlab,
  base.desc = "test series",
  compare.desc = paste0("refit with ", plotting.forecast$method),
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="% over ts span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)
accuracy(plotting.forecast, seis.h.test)
qqPlot(plotting.model[,5])

bptests <- data.frame(lag=integer(), `p-value`=numeric())
for (i in 1:10){
  bptests[nrow(bptests) + 1, ] <- c(i, Box.test(plotting.model[,5], lag = i, fitdf = 0, type = "Box-Pierce")$p.value)
}
bptests.plot <- 
  ggplot(bptests, aes(lag, `p.value`), pch="o") + 
    geom_point() + ylim(0,1) +
    labs(title="Box-Pierce tests for lags 1 to 10") +
    geom_hline(yintercept=0.05, linetype="dotted", color = "blue") +
    scale_x_continuous(breaks=1:10)
bptests.plot

```{r eval=FALSE, include=FALSE}
gc()
if (name == "MEM") {
  proj_file <- 'proj.mems.RData'
  save.image(paste0("/media/data/Documents/Uni/spatiotemp/villalobos/project/", proj_file))
  remove(proj_file)
}
```

>>>>

```{r "libraries", include=FALSE}
library(knitr)
opts_chunk$set(warning = F, message = F)
library(stringi) # %s+%
library(lubridate) # floor_date
library(xts) # zoo
library(fpp) # auto.arima
library(ggplot2)
# library(gridExtra) # for gg-plotting multiple plots
library(cowplot) # for plot_grid
# library(car) # qqPlot
library(qqplotr) # qqplot with ggplot
library(tidyverse) # map_df, read_csv, group_by, summarize
library(tsbox) # https://cran.r-project.org/web/packages/tsbox/vignettes/tsbox.html
```

```{r "initial setup", include=FALSE}
print_dec <- function(x, decimals=2) trimws(format(round(x, decimals), nsmall=decimals))

setwd("/media/data/Documents/Uni/spatiotemp/villalobos/project/")
if (!exists("domain")) {
  # UCCS
  domain <- c(-350000,350000); pattern <- "UCCS.*\\.csv"; name <- "UCCS"; description <- "Uccle, Bruxelles"; proj_file <- 'proj.uccs.RData'
  # MEMS
  domain <- c(-7200,7200); pattern <- "MEM.*\\.csv"; name <- "MEM"; description <- "Membach"; proj_file <- 'proj.mems.RData'
}
if (exists("proj_file")) {
  #load(paste0("/media/data/Documents/Uni/spatiotemp/villalobos/project/", proj_file))
  # save.image(paste0("/media/data/Documents/Uni/spatiotemp/villalobos/project/", proj_file))
}

gg_qqplot <- function(dataset) {
  if (is.ts(dataset))
    dataset <- as.numeric(dataset)
  ggplot(data.frame(values=dataset), aes(sample=values)) +
    stat_qq_band() + stat_qq_line(col="red") + stat_qq_point(shape = 1, size = 3) +
    xlab("Theoretical quantiles (95% conf.)")
}
```

```{r "import dataset", include=FALSE}
seis <-
  list.files(path="csv/", pattern=pattern) %>%
  map_df(~read_csv("csv/" %s+% .))

@@

block_start <- NULL
block_end <- NULL
blocks <- data.frame(start=integer(), end=integer())
for (i in 1:length(seis.missing.ids)) {
  if (is.null(block_start)) {
    block_start <- seis.missing.ids[i]
    block_end <- seis.missing.ids[i]
  } else if ((block_end + 1) == seis.missing.ids[i]) {
    block_end <- seis.missing.ids[i]
  } else {
    blocks[nrow(blocks) + 1, ] <- c(block_start, block_end)
    block_start <- seis.missing.ids[i]
    block_end <- seis.missing.ids[i]
  }
}
blocks[nrow(blocks) + 1, ] <- c(block_start, block_end)
blocks$interval <- hours(blocks$end - blocks$start + 1)
blocks$start <- seis.first.second + hours(blocks$start)
blocks$end <- seis.first.second + hours(blocks$end)
plot(c(rbind(blocks$start, blocks$end, NA)), rep(hour(blocks$interval), each=3),
     col=ifelse(blocks$interval<3600, "darkgreen", "darkred"),
     main="Consecutive hours of missing values",
     ylab="Hours", xlab="Interval start",
     type="l", lwd=10,
     xaxt="n", xlim=c(min(seis$utc_second), max(seis$utc_second))
     )
axis.POSIXct(1, at=seq.POSIXt(from=min(seis$utc_second), to=max(seis$utc_second), by = "1 month"), format="%m-%y", cex=0.8)
text(x=blocks$start, y=hour(blocks$interval), labels = paste0(format(blocks$start, "%y-%m-%d %H:%M")), cex=0.9, pos=2)
text(x=blocks$end, y=hour(blocks$interval), labels = paste0(format(blocks$end, "%y-%m-%d %H:%M")), cex=0.9, pos=4)
text(x=blocks$start + make_difftime(hour=sapply(hour(blocks$interval), "/", y=2)), y=hour(blocks$interval), labels = paste0(hour(blocks$interval), "H"), cex=0.9, pos=3)
text(x=blocks$start + make_difftime(hour=sapply(hour(blocks$interval), "/", y=2)), y=hour(blocks$interval), labels = paste0(hour(blocks$interval), "H"), cex=0.9, pos=1)
remove(seis.complete, seis.missing.ids)

@@

```{r periodgram}
library(spec)
pgram <- spec.pgram(seis.h.train, main="periodgram", detrend=F, demean=T, na.action=na.aggregate)
topfreq <- pgram$freq[order(pgram$spec, decreasing = T)][1:100]
topseas <- 1/topfreq
topseas.h <- topseas/1

filter_freq <- (pgram$spec > (mean(pgram$spec) + sd(pgram$spec)*2)) 
top95pc <- pgram$spec[filter_freq]
top95freq <- pgram$freq[filter_freq][order(top95pc, decreasing = T)]
top95pc <- pgram$spec[filter_freq][order(top95pc, decreasing = T)]
top95seas.s <- 1/top95freq
top95seas.s
top95seas.h <- top95seas.s/1
top95pc/sd(pgram$spec)
top95seas.h

ylims <- 10^par("usr")[3:4]
axis(side=3, at=top95freq, labels=as.integer(top95seas.h), padj = 1, las=2, cex.axis=0.8)
abline(h=mean(pgram$spec) + sd(pgram$spec)*c(.3,1:3), lty="dotted", col=c("orange", "darkgreen", "blue", "red"))
for (i in 1:length(top95freq)) {
  color <- ifelse(top95pc[i] > (mean(pgram$spec) + sd(pgram$spec)*3), "red", ifelse(top95pc[i] > (mean(pgram$spec) + sd(pgram$spec)*2), "blue", ifelse(top95pc[i] > (mean(pgram$spec) + sd(pgram$spec)*1), "darkgreen", "orange")))
  lines(x=c(top95freq[i], top95freq[i]), y=c(top95pc[i],ylims[2]), lty="dotted", col=color)
  points(x=top95freq[i], y=top95pc[i], col=color)
}
axis(side=4, at=mean(pgram$spec) + sd(pgram$spec) * c(.3, 1:3), labels=c(".3", "1", "2", "3"), cex.axis=0.8)
mtext(side=4, "spectrum sd ratio", line=1)
gc()
```

@@
